Analysis Stand Features 

### 2017-05-15 analysis/analysis_stand_features.Rmd
updating

  cat("SUMMARY VALUES \n")
  print(out$summ_comparison) 
  cat("\n")

@@

topo_summary <- topo %>%
  group_by(site) %>%
  summarise(mde_m = mean(mde),
            mde_sd = sd(mde),
            mde_min = min(mde),
            mde_max = max(mde),
            slope_m = mean(slope),
            slope_sd = sd(slope))

# Another way to obtain summary values 
variables <- c('mde','slope','aspect')
auxdf <- data.frame()

for (i in variables){ 
aux <- topo %>% 
  dplyr::group_by(site) %>% 
  summarise_each_(funs(mean, sd, se=sd(.)/sqrt(n())), i) %>% mutate(variable=i)

auxdf <- rbind(auxdf, aux) }
```

@@

### Min & max mde

>>>>

  cat("SUMMARY VALUES \n")
  print(as.data.frame(out$summ_comparison))
  cat("\n")

@@

# 
# topo_summary <- topo %>%
#   group_by(site) %>%
#   summarise(mde_m = mean(mde),
#             mde_sd = sd(mde),
#             mde_min = min(mde),
#             mde_max = max(mde),
#             slope_m = mean(slope),
#             slope_sd = sd(slope))
# 
# 
# 
# # Another way to obtain summary values 
# variables <- c('mde','slope','aspect')
# auxdf <- data.frame() 
# 
# for (i in variables){ 
# aux <- topo %>% 
#   dplyr::group_by(site) %>% 
#   summarise_each_(funs(mean, sd, se=sd(.)/sqrt(n())), i) %>% mutate(variable=i) 
# 
# auxdf <- rbind(auxdf, aux) }
```

@@
